%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% \input{glyphtounicode} % Commented out as this file might not exist in your docker image and can cause errors. Uncomment if you have this file and need it.


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large % Section titles are large and small caps
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{ % List items (like descriptions) are small
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\ % Main subheading bold (default size), secondary small italic
    \textit{\small#3} & \textit{\small #4} \\ % Tertiary info small italic
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\ % Sub-subheading items small italic
    \end{tabular*}\vspace{-7pt}
}

% --- MODIFIED THIS COMMAND for consistency ---
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\ % Project Title bold (default size), Dates small italic (consistent with resumeSubheading)
    \end{tabular*}\vspace{-7pt}
}
% --- End of Modification ---

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}} % Sub-items reuse resumeItem format (small)

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Priyanshu Gupta} \\ \vspace{1pt} % Name is Huge
  \small 8800295258 $|$ \href{mailto:pg0000742@gmail.com}{\underline{pg0000742@gmail.com}} $|$ % Contact info is small
  \href{https://www.linkedin.com/in/priyanshu-gupta-4ba240259}{\underline{linkedin.com/in/priyanshu-gupta-4ba240259}} $|$
  \href{https://github.com/PriyanshuGupta1102}{\underline{github.com/PriyanshuGupta1102}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
  \resumeSubHeadingListStart
    \resumeItem{A passionate and proficient Full-Stack Developer dedicated to building efficient and intuitive applications. I enjoy coding, contributing to the open-source community, and am committed to continuous learning and development.} % Uses \small
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Guru Tegh Bahadur Institute of Technology}{New Delhi, IN} % Bold / Small Italic
      {B.Tech Computer Science and Engineering}{Nov. 2022 -- May 2026} % Small Italic / Small Italic
      \resumeSubItem{Current Percentage: 88.07\%} 
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Internships}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SFP Education and Technology Pvt Ltd|IT/Computers-Software}{June 2024 -- Aug 2024} % Bold / Small Italic
      {Full Stack Web Developer}{ } % Small Italic / Small Italic (Empty here)
      \resumeItemListStart
        \resumeItem{Contributed to the development of full-stack web applications utilizing technologies such as React and Node.js.} % Uses \small
        \resumeItem{Gained practical experience in front-end development by building user interfaces with HTML, CSS, and JavaScript.} % Uses \small
       
      \resumeItemListEnd

      \resumeSubheading
      {RS Barcoders Pvt Ltd|IT/Computers-Software}{Jul 2024 -- Aug 2024} % Bold / Small Italic
      {Software Tester}{ } % Small Italic / Small Italic (Empty here)
      \resumeItemListStart
        \resumeItem{Contributed to the quality assurance of a large-scale Warehouse Management System (WMS), focusing on ensuring the reliability of core inventory and order processing modules.} % Uses \small
        \resumeItem{Executed detailed Manual Testing cases to verify system functionality, identify UI defects, and ensure adherence to business requirements.} % Uses \small
        \resumeItem{Assisted the development team by writing and maintaining Unit Testing scripts to validate individual functions and prevent regressions in the codebase.} % Uses \small
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{%
  \href{https://github.com/PriyanshuGupta1102/e-commerce-react}{%
    {\small\textbf{Front-End E-commerce Page} $|$ \emph{React.js, Jest, React Testing Library, CSS}}%
  }%
}{July 2025 -- July 2025}
      \resumeItemListStart
        \resumeItem{The goal of this project was to ensure the quality of a user-facing e-commerce product page built with React.} % Uses \small
        \resumeItem{ I took a two-pronged approach: first, I performed manual exploratory testing to understand the application like a real user would, and second, I built an automated unit test suite to create a long-term safety net against regressions.} % Uses \small
        \resumeItem{During the manual testing phase, I used browser developer tools to simulate different devices and to prevent future bugs in the application's logic, I used Jest and React Testing Library to write automated unit tests. The philosophy of React Testing Library is to test the application the way a user would use it, so I wrote tests that would find elements by their text or label.} % Uses \small
      \resumeItemListEnd
\resumeProjectHeading{%
  \href{https://github.com/PriyanshuGupta1102/node-auth-api}{%
    {\small\textbf{Back-End Authentication API} $|$ \emph{Node.js, Express.js, JWT (JSON Web Tokens), Postman}}%
  }%
}{July 2025 -- July 2025} % Bold / Small Italic fix
      \resumeItemListStart
        \resumeItem{The objective of this project was to validate the security, reliability, and functionality of a critical back-end service: a RESTful authentication API built with Node.js and Express.} % Uses \small
        \resumeItem{My primary responsibility was to ensure that the API's business logic was sound and that it handled data securely. I started with manual API testing using Postman to explore the endpoints, then I developed a complete automated integration test suite to formalize these checks.} % Uses \small
        \resumeItem{Using Postman, I manually tested every endpoint to verify the core business rules and to automate these checks, I used Jest and Supertest.} % Uses \small
      \resumeItemListEnd
\resumeProjectHeading{%
  \href{https://github.com/PriyanshuGupta1102/task-api}{%
    {\small\textbf{Task Management System API} $|$ \emph{Java, Spring Boot, Spring Data JPA, H2 Database}}%
  }%
}{July 2025 -- July 2025} % Bold / Small Italic
      \resumeItemListStart
        \resumeItem{For this project, I engineered a quality assurance plan for a full CRUD (Create, Read, Update, Delete) REST API in an enterprise-level environment using Java and Spring Boot.} % Uses \small
        \resumeItem{The key challenge here was to test the API's logic in isolation. My strategy was to use manual testing with Postman for initial validation, followed by building a suite of true automated unit tests using standard Java testing frameworks.} % Uses \small
        \resumeItem{Using Postman, I validated the entire CRUD lifecycle. I confirmed that POST requests created new tasks, GET requests retrieved them, PUT updated them, and DELETE removed them. Most importantly, I verified the correct HTTP status codes were returned for each operation, such as 201 Created, 204 No Content for deletion, and 404 Not Found for non-existent tasks.} % Uses \small
        \resumeItem{The core of this project was writing isolated unit tests for the TaskController. This is a professional practice that ensures tests are fast and only test one thing at a time.} % Uses \small
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeSubHeadingListStart % Entire block is small
    \resumeItem {\textbf{Programming Languages}{: HTML5, CSS3, JavaScript, SQL, Python, Java, C, C++}} \\ % Category bold (within small)}
    \resumeItem {\textbf{Web Technologies}{: Git, MySQL, Material-UI, React.js, Express.js, Node.js, MongoDB}} \\ % Category bold (within small)
    \resumeItem {\textbf{Developer Tools}{: Docker, Jetbrains Webstorm, VS Code, IntelliJ Idea} }\\ % Category bold (within small)
    \resumeItem {\textbf{Data Science}{: Numpy, Pandas, Matplotlib}} \\ % Category bold (within small)
    \resumeItem {\textbf{Artificial Intelligence}{: Gemini, Google GenAI}} \\ % Category bold (within small)
    \resumeItem {\textbf{Other}{: \href{https://github.com/PriyanshuGupta1102/DSA-QUESTIONS}{Data Structures and Algorithms}}}
\end{itemize}

%-------------------------------------------
\end{document}
